Perturbing the catalase active site electric field via genetic code expansion

### 2018-03-18 bb494/manuscript.tex
Add conclusion section.

\subsection*{Conclusion}

ncAA substitution is a powerful technique which allows easy testing of hypotheses in regions which are very sensitive to structural change. This technique could be used to test -other-catalase-hypotheses-.\\

Perhaps this technique could be used to study e-fields generally.\\

We propose that the following residues be incorporated into the channel at sites - - -. Coupled with APBS simulations, these results could be a powerful test of the effects of catalase e-field.\\

>>>>

\subsection*{Conclusions}
Noncanonical amino acid substitution allows much more precise atom-level perturbation of protein structure than residue-level mutagenesis. This is an emerging tool which can be used to study phenomena not reachable in the past. Here we demonstrate how the tool can be used to study the electric field in catalase, and propose a larger scale study which could definitely show the importance of electric field. The use of electrostatic simulations provides a theoretical explanation for the results seen after mutagenesis. By combining theory with atom-level perturbations, much can be learned about protein electrostatics.
